% Robbie Perlstein's resume - 02/13/2013


\documentclass[line,margin]{res}
\paperwidth=8.5in
\paperheight=11.5in
\usepackage{tabto}

% Adjust margin locations
\addtolength{\oddsidemargin}{-10px}

% Constant formatting parameters
\newcommand{\bulletOne}{85px}
\newcommand{\bulletTwo}{155px}
\newcommand{\bulletThree}{225px}
\newcommand{\bulletFour}{305px}
\newcommand{\experienceTitleFormat}{10px}




\begin{document}

\newlength\mywidth
\setlength\mywidth\textwidth
\addtolength\mywidth{\sectionwidth}

\name{\huge Robbie Perlstein\vspace{2px}}
\address{1416 Pennsylvania St \#3, Denver, CO 80203}
\address{561-751-7992 | robbie.perlstein@gmail.com}


\begin{resume}
\vspace{5px}
\section{PERSONAL STATEMENT}	
After trying on many hats, I accepted the calling I ignored in my earlier days - software development. I love to solve problems and live to develop software. My first job as a Java developer has shaped me in an important way - I understand the software development life cycle, can work under strict time constraints, and thrive in situations laden with uncertainty by forging my own path and completing business objectives.

\section{EDUCATION}	
{\sl Bachelor of Science,} Computer Science and Engineering
\\ University of Colorado, Denver
\\ Expected graduation: May 2014
\\ GPA - 3.842
\\

\section{TECHNICAL SKILLS} 
LANGUAGES: 
\tabto{\bulletOne} 	\textbullet{  C++ } 
\tabto{\bulletTwo} 	\textbullet{  Java  }  
\tabto{\bulletThree}	\textbullet{  Python  }  
\tabto{\bulletFour}	\textbullet{  Jython  }
\vspace{5px}
\\ TECHNOLOGY:  
\tabto{\bulletOne} 	\textbullet{  JUnit 3.x }  
\tabto{\bulletTwo} 	\textbullet{  JBoss 4.x  }  
\tabto{\bulletThree}	\textbullet{  Apache Ant  }  
\tabto{\bulletFour}	\textbullet{  Subversion  }
\\
\vspace{1px}
\tabto{\bulletOne} 	\textbullet{  Git } 
\tabto{\bulletTwo} 	\textbullet{  UNIX } 
\tabto{\bulletThree} \textbullet{  Eclipse Modeling Framework } 
\\

\section{RELAVANT EXPERIENCE}
ENODIA FINANCIAL TECHNOLOGY \hfill June 2012 - Dec 2012 \\
{\sl Jr. Java Developer}
\begin{itemize}
\vspace{2px}
\item Developed real-time, server-side financial reporting software for Tradition Asiel Securties as part of Enodia Financial's FIX protocol trading platform in compliance with the Dodd–Frank Wall Street Reform and Consumer Protection Act.
\item Developed trade reporting technologies for the London Stock Exchange's Turquiose trading group under similar requirements as Tradition Asiel Secuities.
\item Maintained legacy code by providing additional functionality, patching fatal bugs, and redesigning outdated workflow models.
\item Java/Jython-based agile workshop focused on test-driven design and iterative development.
\end{itemize}


\section{NOTABLE EMPLYOMENT HISTORY}
THE UPS STORE \hfill OCT 2008 - AUG 2009 \\
{\sl ASSITANT MANAGER}
\begin{itemize}
\vspace{2px}
\item Assistant Manager of the highest volume UPS Store in Colorado.
\item Duties include cashiering, telephone reception (incoming and outgoing), management of over 350 mailbox service accounts, sales, solving people’s shipping and packaging needs, insurance claims, a lot of heavy lifting, and numerous specialized tasks.
\end{itemize}

INFOWORX \hfill JAN 2002 - AUG 2005 \\
{\sl PRODUCTION COORDINATOR}
\begin{itemize}
\vspace{2px}
\item Assisted in production of five large-scale infomercials and over a dozen smaller “Direct Response” 1 to 2 minute spots, including iRobot's Roomba robotic vacuum, Lean Bean, Ashley Skin Nutrition, Vibrassage, and Shangrila Multi Brew.
\item Conducted product research and created advertising solutions. Managed petty cash, office management, product support, client relations, and in-house IT issues.
\end{itemize}


\end{resume}

\end{document}
